### 2023-11-06 paper/content.tex

Several branches of Earth Sciences have demonstrated the importance of spatial resolution on a microscopic scale. For example, geochemistry and
geochronology applications have benefited from point-wise analyses
and compositional maps, allowing significant advances in the understanding of
igneous, metamorphic and sedimentary processes \citep{Verberne2020, Barnes2019,
Davidson2007}. Classical paleomagnetic techniques, on the other hand, consist
of analyzing bulk samples, where the magnetic signal of a single specimen is
the result of the sum of moments of a large assembly of ferromagnetic grains
\citep{Dunlop1997}. Typically, a standard paleomagnetic sample of
approximately \qty{10}{\cm\cubed} would contain hundreds of thousands
to millions of magnetic particles with sizes varying from magnetically stable
single-domain (SD) and vortex state grains (also called pseudo-single domain,
PSD) with sizes below \qty{1}{\um}, to large ($\gg \qty{1}{\um}$) grains with
multi-domain (MD) magnetic structures, which are less stable magnetic recorders
\citep{Berndt2016}. These large MD grains usually conceal the signal of the SD
and PSD grains, and techniques of step-wise thermal and magnetic treatments are
needed to unveil this more stable and reliable magnetic record
\citep{Tauxe2018}. Recently, magnetic microscopy techniques opened the
possibility of obtaining magnetic field maps at the micro-scale and recovering the
magnetization of each grain, therefore enabling the separate analysis of stable
and unstable magnetic particles \citep{DeGroot2018, Lima2014, Weiss2007,
DeGroot2014}.

@@

\begin{equation}
x_c \partial_x f + y_c \partial_x f + z_c \partial_x f + \eta b
=
x \partial_x f + y \partial_y f + z \partial_z f + \eta f
\ .
\end{equation}

@@

\begin{equation}
\label{eq_vector_to_incdec}
\begin{aligned}
I &= \tan^{-1}\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}} \ , \\
D &= \tan^{-1}\dfrac{m_x}{m_y} \ , \\
m &= \sqrt{m_x^2 + m_y^2 + m_z^2} \ .
\end{aligned}
\end{equation}

@@

To simulate particles with non-dipolar magnetization components, we specified a spherical volume with a radius of approximately \qty{1}{\um}.
Within this volume, we added 200 dipolar particles with varying dipole moment directions and amplitudes.
These directions were generated randomly, following a normal distribution centered on the direction $D=\ang{90}$ and $I=\ang{0}$ and with a standard deviation of \ang{10}.
The dipole moment amplitudes were sampled by a normal distribution with mean $\qty{e-14}{\ampere\m\squared}$ and standard deviation $\qty{5e-14}{\ampere\m\squared}$.
We also randomly generated spatial positions around a central position of $x_c=\qty{25}{\um}$, $y_c=\qty{25}{\um}$, and $z_c=\qty{-1}{\um}$ with standard deviation of \qty{0.65}{\um}.
The bulk magnetization of the non-dipolar particle is the vector sum of the dipole moments of each dipole.
The centroid of the particle is defined by the average of the $x_c$, $y_c$, and $z_c$ positions of each dipole.
The synthetic vertical magnetic field $b_z$ of the non-dipolar source was calculated on regular grids with \qty{0.5}{\um} spacing.
Each grid was located at a different sensor-sample distance $z$, varying between \qty{1}{\um} and \qty{10}{\um} in \qty{0.5}{\um} increments.
The synthetic data were corrupted by pseudo-random Gaussian noise of mean \qty{0}{\nano\tesla} and a standard deviation of \qty{20}{\nano\tesla}.
For each data grid generated, we performed Euler deconvolution to estimate the source position and subsequently inverted the data for the dipole moment.
At each step, we recorded the inversion $R^2$ value and the differences between the estimated position and dipole moment and the true centroid and bulk magnetization of the particle.

@@

We replicated the particle generation procedure 100 times with variations in the randomness of magnetization and point particle positions. Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data. The effectiveness of position recovery was measured by comparing the particle's centroid with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively). As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero. However, when the sensor-source distance is small enough to emphasize the contribution from higher-order components, a lower degree of dipolarity is observed as expressed by lower values of $R^2$ (Figure~\ref{non-dipolarity-synthetic-data-inversion}a). Consequently, in these cases, there are higher errors in the estimation of the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which were expected since the inversion considers only the dipolar component. However, dipolarity significantly increases as the sensor to sample distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/non-dipolarity-synthetic-positioning.png}
  \caption{The simulation was randomly replicated (N=100) to test the effectiveness of the Euler deconvolution in estimating the position of the modeled particles. The difference between the true position (centroid) and the estimated position was calculated for each replicate and plotted as a boxplot. The boxplot shows the distribution of differences in the (a) $x_c$, (b) $y_c$, and (c) $z_c$.}
  \label{non-dipolarity-synthetic-data-positioning}
\end{figure}

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/non-dipolarity-synthetic-inversion.png}
  \caption{The simulation was randomly replicated (N=100) to assess the accuracy of the algorithm in recovering the magnetic direction and moment of the modeled particles. The goodness of fit was measured by the R-squared value (a), while the angular error (b) and intensity error (c) between the real and modeled magnetic vector were plotted in degrees and percentages ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$), respectively.}
  \label{non-dipolarity-synthetic-data-inversion}
\end{figure}

@@

For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensities.
The depths vary randomly between 1 and $\qty{20}{\um}$, while the dipole moment intensities range randomly from $10^{-12}$ to $\qty{e-14}{\ampere\m\squared}$.
The NRM found in real ferromagnetic particles varies individually but averages out to the inducing field direction.
To simulate this behavior in our synthetic data, we sample the source dipole moment directions from two pseudo-random Gaussian distributions.
The first group of sources ($M = 70$) are sampled from a distribution  with mean of $D = \ang{0}$ and $I = \ang{0}$ and standard deviation of $\ang{10}$.
The second group of sources ($M = 30$) are sampled from a distribution with mean of $D = \ang{180}$ and $I = \ang{0}$, also with standard deviation of $\ang{10}$. We also manually added 3 sources with higher dipole moments ($5x10^{-11}$) to further simulate the complexity observed in real data measurements. The noise-corrupted synthetic $b_z$ data are shown in Figure~\ref{complex-synthetic-data}a.

@@

We then followed the same processing steps as for the simple synthetic: upward continuation (Figure~\ref{complex-synthetic-data}b),
TGA calculation (Figure~\ref{complex-synthetic-data}c), contrast stretching (Figure~\ref{complex-synthetic-data}d), blob detection (Figure~\ref{complex-synthetic-data}e), and Euler Deconvolution (Figure~\ref{complex-synthetic-data}e).
A total of 99 sources out of the original 103 were successfully detected by our workflow.

\begin{figure}[tb!]
\centering
\includegraphics[width=0.75\linewidth]{figures/complex-synthetic-comparison.png}
\caption{
The validation of the result obtained with the inversion was calculated for each individual particle based on the error between the real parameters modeled and their respective recovered values, being (a) the direction and (b) intensity of the magnetic moment, in addition to the $R^2$ score (c) obtained by comparing the forward model and the actual data. The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - 20 $\mu m$) and the horizontal bar by the dipole moment amplitude ($10^{-12}$ to $10^{-14}$ $Am^2$).
}
\label{complex-synthetic-comparison}
\end{figure}

@@

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately $\qty{1410}{\um} \times \qty{2256}{\um}$ (Figure~\ref{real-data}a) with a grid
spacing of \qty{2.35}{\um} and a sensor-sample distance of approximately \qty{5}{\um}, totaling
576,000 data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy (PMM) mode and converted to the vertical component of magnetic field ($b_z$) using a spectral approach \citep{Lima2009, Fu2020,
Glenn2017}. We applied a bias field of \qty{0.9}{\milli\tesla} during the measurement, which was periodically reversed to result in an effective background field of $< \qty{1}{\micro\tesla}$.  After applying the magnetic anomaly detection algorithm (Figure~\ref{real-data}b-e), it was
possible to determine the windows for 75 potential sources, as shown in Figure~\ref{real-data}e.

@@

After applying the ED algorithm, we performed the inversion of the magnetic moment for each of the 75 windows selected previously. In order to reduce considerably the computation time, the inversions were done within each data window, instead of solving all sources parameters at the same time. We obtained the magnetic moment and the direction for all 75 magnetic grains (Figure~\ref{real-data-stereograms}a). Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination $R^2$ and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained. We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than 5. An $R^2$ value of 0.85 indicates that \qty{85}{\percent} of the measured magnetic data is explained by the predicted dipole model, which is equivalent to the dipolarity test approach \citep{Fu2020}. On the other hand, an SNR of 5 means that the dipolar signal is 5 times greater than the residual noise. By using these criteria, we ensured that the fit was sufficiently accurate and the dipole model provided a reliable approximation of the original magnetic data. About 46 identified sources passed these criteria. This filtering technique removed the poorly fit predicted models as well as the ones too corrupted with noise, showing more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b). Notably, it is confirmed that the sample has both magnetic minerals, but by the expected directions we can also stipulate that the magnetite grains outnumber the hematite ones.

@@

Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible.
One way to circumvent the ambiguity is to incorporate prior information about the subsurface structure, such as the positioning of a known source of magnetization.
Magnetic field measurements are more sensitive to changes in magnetization near the source that is causing the anomaly.
When the position of the source is known, it constrains the model to be as consistent as possible with the observed data, hence increasing the likelihood of obtaining unique solutions.
\citet{Oliveira2015Estimation} proved that the magnetization directions (Dec and Inc) recovered by the least squares estimator are sensitive to great variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
Thus, they consider the ED method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
This occurs mainly because, when well performed, the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
This remark is also better observed in our simple synthetic sample where the estimated horizontal positions slightly deviate from the true values, which implies small misfit values in the recovered magnetic directions.
Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the depth of the source, which is probably caused by ambiguities.
In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise since that high-frequency noise sensibility is one of the ED's main limitations.

@@

Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for the purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial domain \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}.
However, this assumption is not always true when dealing with complex samples (i.e., more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples.
The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021}.
The latter further allows unique estimation of magnetic moment configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}.
Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with the weaknesses of the additional method used.
The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals, as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
In any case, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.

@@

The total gradient anomaly (TGA) might be considered the ideal image to be used as input for the LoG blob detection algorithm for potential field studies (micro and/or macroscale).
The TGA highlights the subsurface sources by generating a map of positive magnetic anomalies concentrated within their edges.
This technique is widely used in aeromagnetic surveys to determine the boundaries of sources by calculating the magnetic gradient in all Cartesian directions and displaying those regions where the gradient has maximum values, which is a local maxima distribution.
Hence. The application for micromagnetic measurements comes with all the advantages and drawbacks previously mentioned because is highly dependent on the selection of a good data window.
Nonetheless, the windows generated isolate the main magnetic signal’s region of each source.
This guarantees that our thresholding approach (see section~\ref{dipole-reliability}), for both ED and dipolar inversion, is performed using the critical slice of the micromagnetic data, giving satisfactory parameters approximation and fast results as shown in the synthetic data.

The complex synthetic data allows better observation of the strengths and limitations of the windows approach.
The main strengths that can be mentioned are: (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a).
(iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).
(iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
The major limitations observed were: (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
(ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
(iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep-seated sources and/or particles with small dipole moments generate worse results, essentially because they will produce weaker anomalous fields in the magnetic maps.
Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor.

>>>>

Several branches of Earth Sciences have demonstrated the importance of spatial resolution on a microscopic scale. For example, geochemistry and
geochronology applications have benefited from point-wise analyses
and compositional maps, allowing significant advances in the understanding of
igneous, metamorphic and sedimentary processes \citep{Verberne2020, Barnes2019,
Davidson2007}. Classical paleomagnetic techniques, on the other hand, consist
of analyzing bulk samples, where the magnetic signal of a single specimen is
the result of the sum of moments of a large assembly of ferromagnetic grains
\citep{Dunlop1997}. Typically, a standard paleomagnetic sample of
approximately \qty{10}{\cm\cubed} would contain hundreds of thousands
to millions of magnetic particles with sizes varying from magnetically stable
single-domain (SD) and vortex state grains (also called pseudo-single domain,
PSD) with sizes below \qty{1}{\um} \citep{Berndt2016}, to large ($\gg \qty{1}{\um}$) grains with
multi-domain (MD) magnetic structures, which are less stable magnetic recorders \citep{Dunlop1997}.
These large MD grains usually conceal the signal of the SD
and PSD grains, and techniques of step-wise thermal and magnetic treatments are
needed to unveil this more stable and reliable magnetic record
\citep{Tauxe2018}. Recently, magnetic microscopy techniques opened the
possibility of obtaining magnetic field maps at the micro-scale and recovering the
magnetization of each grain, therefore enabling the separate analysis of stable
and unstable magnetic particles \citep{DeGroot2018, Lima2014, Weiss2007,
DeGroot2014}.

@@

\begin{equation}
x_c \partial_x f + y_c \partial_y f + z_c \partial_z f + \eta b
=
x \partial_x f + y \partial_y f + z \partial_z f + \eta f
\ .
\end{equation}

@@

\begin{equation}
\label{eq_vector_to_incdec}
\begin{aligned}
I &= \tan^{-1}\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}} \ , \\
D &= \tan^{-1}\dfrac{m_y}{m_x} \ , \\
m &= \sqrt{m_x^2 + m_y^2 + m_z^2} \ .
\end{aligned}
\end{equation}

@@

To simulate particles with non-dipolar magnetization components, we specified a spherical volume with a radius of approximately \qty{1}{\um}.
Within this volume, we added 200 dipolar particles with varying dipole moment directions and amplitudes.
These directions were generated randomly, following a normal distribution centered on the direction $D=\ang{90}$ and $I=\ang{0}$ and with a standard deviation of \ang{10}.
The dipole moment amplitudes were sampled by a normal distribution with mean $\qty{e-14}{\ampere\m\squared}$ and standard deviation $\qty{5e-14}{\ampere\m\squared}$.
We also randomly generated spatial positions around a central position of $x_c=\qty{25}{\um}$, $y_c=\qty{25}{\um}$, and $z_c=\qty{-1}{\um}$ with standard deviation of \qty{0.65}{\um}.
The bulk magnetization of the non-dipolar particle is the vector sum of the dipole moments of each dipole.
The centroid of the spherical volume is defined by the average of the $x_c$, $y_c$, and $z_c$ positions of each dipole.
The synthetic vertical magnetic field $b_z$ of the non-dipolar source was calculated on regular grids with \qty{0.5}{\um} spacing.
Each grid was located at a different sensor-sample distance $z$, varying between \qty{1}{\um} and \qty{10}{\um} in \qty{0.5}{\um} increments.
The synthetic data were corrupted by pseudo-random Gaussian noise of mean \qty{0}{\nano\tesla} and a standard deviation of \qty{20}{\nano\tesla}.
For each data grid generated, we performed Euler deconvolution to estimate the source position and subsequently inverted the data for the dipole moment.
At each step, we recorded the inversion $R^2$ value and the differences between the estimated position and dipole moment and the true centroid and bulk magnetization of the spherical particle.

@@

We replicated the particle generation procedure 100 times with variations in the randomness of magnetization and point particle positions. Subsequently, the Cartesian position of the spherical particle was estimated using ED, and the magnetization parameters were determined by inverting the magnetic field data. The effectiveness of position recovery was measured by comparing the centroid of the spherical volume with the solution of the Euler equation for $x_c$, $y_c$, and $z_c$ (Figure~\ref{non-dipolarity-synthetic-data-positioning}a, b, and c, respectively). As shown in Figure~\ref{non-dipolarity-synthetic-data-positioning}, ED estimates the positions of particles with more complex magnetization well, especially for sensor-source distances greater than 5 µm, where the median of the distributions is centered at zero. However, when the sensor-source distance is small enough to emphasize the contribution from higher-order components, a lower degree of dipolarity is observed as expressed by lower values of $R^2$ (Figure~\ref{non-dipolarity-synthetic-data-inversion}a). Consequently, in these cases, there are higher errors in the estimation of the direction of magnetization (Figure~\ref{non-dipolarity-synthetic-data-inversion}b) and in the magnetic moment's intensity (Figure~\ref{non-dipolarity-synthetic-data-inversion}c), which were expected since the inversion considers only the dipolar component. However, dipolarity significantly increases as the sensor to sample distance increases, while errors in direction and magnetic moment decrease significantly (Figure~\ref{non-dipolarity-synthetic-data-inversion}).

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/non-dipolarity-synthetic-positioning.png}
  \caption{The simulation was randomly replicated (N=100) to test the effectiveness of the Euler deconvolution in estimating the position of the modeled particles. The difference between the true position (centroid) and the estimated position was calculated for each replicate and plotted as a boxplot. The boxplot shows the distribution of differences in the (a) $x_c$, (b) $y_c$, and (c) $z_c$. The black dots represent outliers in the distributions.}
  \label{non-dipolarity-synthetic-data-positioning}
\end{figure}

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/non-dipolarity-synthetic-inversion.png}
  \caption{The simulation was randomly replicated (N=100) to assess the accuracy of the algorithm in recovering the magnetic direction and moment of the modeled particles. The goodness of fit was measured by the R-squared value (a), while the angular error (b) and intensity error (c) between the real and modeled magnetic vector were plotted in degrees and percentages ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$), respectively. The black dots represent outliers in the distributions.
}
  \label{non-dipolarity-synthetic-data-inversion}
\end{figure}

@@

For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensities.
The depths vary randomly between 1 and $\qty{20}{\um}$, while the dipole moment intensities range randomly from $10^{-11}$ to $\qty{e-14}{\ampere\m\squared}$.
The NRM found in real ferromagnetic particles varies individually but averages out to the inducing field direction.
To simulate this behavior in our synthetic data, we sample the source dipole moment directions from two pseudo-random Gaussian distributions.
The first group of sources ($M = 70$) are sampled from a distribution  with mean of $D = \ang{0}$ and $I = \ang{0}$ and standard deviation of $\ang{10}$.
The second group of sources ($M = 30$) are sampled from a distribution with mean of $D = \ang{180}$ and $I = \ang{0}$, also with standard deviation of $\ang{10}$. We also manually added 3 sources with higher dipole moments ($5$x$10^{-11}$) to further simulate the complexity observed in real data measurements. The noise-corrupted synthetic $b_z$ data are shown in Figure~\ref{complex-synthetic-data}a.

@@

We then followed the same processing steps as for the simple synthetic: upward continuation (Figure~\ref{complex-synthetic-data}b),
TGA calculation (Figure~\ref{complex-synthetic-data}c), contrast stretching (Figure~\ref{complex-synthetic-data}d), blob detection (Figure~\ref{complex-synthetic-data}e), and Euler Deconvolution (Figure~\ref{complex-synthetic-data}e).
A total of 99 sources out of the original 103 were successfully detected in approximately 8 seconds by our algorithm. It further determined the 3D positions and dipole moments of these sources in just 1.5 seconds, all while running on an Intel(R) Core(TM) i7-2670QM CPU 2.20GHz with 16 GB of DDR3L 1333 MHz RAM. Four sources remained unidentified (black stars, Figure~\ref{complex-synthetic-data}f) due to specific challenges, that arose from two primary factors. First, three of these sources either were overlapped by or were in close proximity to other neighboring sources, making it inherently difficult to distinguish and isolate them. Second, the identification of one of these sources was impeded by its considerable depth, which led to substantial signal attenuation, further exacerbating the difficulties associated with source recognition.

\begin{figure}[tb!]
\centering
\includegraphics[width=0.75\linewidth]{figures/complex-synthetic-comparison.png}
\caption{
The validation of the result obtained with the inversion was calculated for each individual particle based on the error between the real parameters modeled and their respective recovered values, being (a) the direction and (b) intensity of the magnetic moment, in addition to the $R^2$ score (c) obtained by comparing the forward model and the actual data. The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - 20 $\mu m$) and the horizontal bar by the dipole moment amplitude ($10^{-11}$ to $10^{-14}$ $Am^2$).
}
\label{complex-synthetic-comparison}
\end{figure}

@@

After remanence acquisition, we performed a magnetic map with the Quantum
Diamond Microscope (QDM) at Harvard University over a sample section of
approximately $\qty{1410}{\um} \times \qty{2256}{\um}$ (Figure~\ref{real-data}a) with a grid
spacing of \qty{2.35}{\um} and a sensor-sample distance of approximately \qty{5}{\um}, totaling
576,000 data points. The QDM is housed in a shielded room, in
order to avoid the influence of the Earth's magnetic field while the data were taken in projected magnetic microscopy mode and converted to the vertical component of magnetic field ($b_z$) using a spectral approach \citep{Lima2009, Fu2020,
Glenn2017}. We applied a bias field of \qty{0.9}{\milli\tesla} during the measurement, which was periodically reversed to result in an effective background field of $< \qty{1}{\micro\tesla}$.  After applying the magnetic anomaly detection algorithm (Figure~\ref{real-data}b-e), it was
possible to determine the windows for 100 potential sources (within 3 seconds), in which 75 were filtered with coherent ED position ($z_c \leq 0$), as shown in Figure~\ref{real-data}e.

@@

In order to reduce considerably the computation time, the ED and magnetic moment inversions were done within each data window, instead of solving all sources parameters at the same time. We obtained (within 2.5 seconds) the position and dipole moment for all 75 magnetic grains (Figure~\ref{real-data-stereograms}a). Then, we calculated the residuals of the inversions in each window and subsequently the coefficient of determination $R^2$ and signal-to-noise ratio (SNR), which were parameters used as filters for the best directions obtained. We considered a good fit to be achieved when $R^2$ was greater or equal to 0.85 and SNR was greater than 5. An $R^2$ value of 0.85 indicates that \qty{85}{\percent} of the measured magnetic data is explained by the predicted dipole model, which is equivalent to the dipolarity test approach \citep{Fu2020}. On the other hand, an SNR of 5 means that the dipolar signal is 5 times greater than the residual noise. By using these criteria, we ensured that the fit was sufficiently accurate and the dipole model provided a reliable approximation of the original magnetic data. About 46 identified sources passed these criteria. This filtering technique removed the poorly fit predicted models as well as the ones too corrupted with noise, showing more clearly the expected directional clusters of hematite and magnetite crystals (Figure~\ref{real-data-stereograms}b). Notably, it is confirmed that the sample has both magnetic minerals, but by the expected directions we can also stipulate that the magnetite grains outnumber the hematite ones.

@@

Working with potential field data might be very tricky once there is too much ambiguity involved during data modeling, thus to obtain unique and reliable results from data inversion it is necessary to provide as much prior information as possible.
One way to circumvent the ambiguity is to incorporate prior information about the subsurface structure, such as the position of a known source of magnetization.
Magnetic field measurements are more sensitive to changes in magnetization near the source that is causing the anomaly.
When the position of the source is known, it constrains the model to be as consistent as possible with the observed data, hence increasing the likelihood of obtaining unique solutions.
\citet{Oliveira2015Estimation} proved that the magnetization directions (Dec and Inc) recovered by the least squares estimator are sensitive to great variations in the horizontal coordinates of the center of the magnetic sources, but are practically insensitive to variations in depth.
Thus, they consider the ED method as an adequate technique to estimate the central positions that will be used as prior information for inversion.
This occurs mainly because, when well performed, the recovery of the source's horizontal coordinates is considerably accurate, while the vertical coordinate can undergo greater variation even though it still provides satisfactory results \citep{Silva20033D, Melo2013}.
This remark is also better observed in our simple synthetic sample where the estimated horizontal positions slightly deviate from the true values, which implies small misfit values in the recovered magnetic directions.
Although the estimated magnetic moment for the said sample is satisfactory, this magnetic parameter is more affected by the variations in the depth of the source, which is probably caused by ambiguities.
In summary, in order to estimate all magnetic parameters as precisely as possible the ED must be executed within a data window containing the lowest amount possible of noise since that high-frequency noise sensibility is one of the ED's main limitations.

@@

Since the pioneering work of \cite{Egli2000}, many methodologies were proposed for solving the inverse problem o micromagnetic data, and for the purpose of comparison we separate them into two categories based on the main estimated parameter by the inversion procedure.
In the first type of approach, the main goal is usually to estimate average magnetization by inverting the whole sample superficial magnetization data commonly by means of unidirectional problem, uniform directions with non-negative variable dipole moments \citep[e.g.,][]{Weiss2007}, including performance enhancement in the spatial domain \citep[e.g.,][]{Myre2019} or frequency domain  \citep[e.g.,][]{Lima2013}.
This methodology can be used to remarkably estimate the average magnetic direction and the total moment direction with the assumption that the particles were all magnetized in the direction of the same induced field \citep[sIRM and/or NRM in basalts,][]{Weiss2007}.
However, this assumption is not always true when dealing with complex samples (i.e., more than one stable direction), which leads to the same drawbacks as the classic paleomagnetic measurements using bulk samples.
The second type of approach has the goal of finding the individual source magnetic properties, which can be done by either inverting the dipole moment of a single source within a cropped section of an upward continued anomaly map \citep[e.g.,][]{Lima2016, Fu2020} or by the insertion of additional information of the sources’ shape, such as micro-computed tomography (microCT) \citep[e.g.,][]{Fabian2019, DeGroot2018, DeGroot2021, Kosters2023}.
The latter further allows unique estimation of magnetic moment configuration of even higher orders components through spherical harmonics expansion constrained by micromagnetic models \citep[e.g.,][]{CortesOrtuno2021, CortesOrtuno2022}.
Such outstanding techniques come with some troubles of having to mechanically select the data for inversion or dealing with the weaknesses of the additional method used.
The MicroCT, for example, is a popular non-destructive technique for high-resolution imaging of the material internal structures, and yet, it is accompanied by some limitations when it comes to paleomagnetic studies: firstly, the technique has a spatial resolution on the order of micrometers, which is not sufficient to directly image the fined grained single-domain magnetite \citep{DeGroot2018}.
The microCT also struggles to discern ferromagnetic (\textit{l.s.}) from non-magnetic/antiferromagnetic minerals (although assigning to them negligible magnetization), as pointed out by \cite{DeGroot2021}, since they usually have similar densities and therefore similar X-ray attenuation \citep{Cnudde2013}.
In any case, the major limitation of microCT lies in the trade-off between the resolution and the sample size, requiring small sample volumes to achieve higher resolutions causing the technique to be too time-consuming.

@@

The total gradient anomaly (TGA) might be considered the ideal image to be used as input for the LoG blob detection algorithm for potential field studies (micro and/or macroscale).
The TGA highlights the subsurface sources by generating a map of positive magnetic anomalies concentrated within their edges.
This technique is widely used in aeromagnetic surveys to determine the boundaries of sources by calculating the magnetic gradient in all Cartesian directions and displaying those regions where the gradient has maximum values, which is a local maxima distribution.
Hence, the application for micromagnetic measurements comes with all the advantages and drawbacks previously mentioned because is highly dependent on the selection of a good data window.
Nonetheless, the windows generated isolate the main magnetic signal’s region of each source.
This guarantees that our thresholding approach (see section~\ref{dipole-reliability}), for both ED and dipolar inversion, is performed using the critical slice of the micromagnetic data, giving satisfactory parameters approximation and fast results as shown in the synthetic data.

The complex synthetic data allows better observation of the strengths and limitations of the windows approach. The main strengths that can be mentioned are: 
% (i) the applied technique not only detects most of the modeled sources but also (ii) most of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a).
% (iii) The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d).
% (iv) Shallow particles grouped in clusters are usually well individualized during window selection, as well as (v) some isolated particles that produce a weak magnetic signal.
\begin{enumerate}[label=\roman*)]
  \item The applied technique detects most of the modeled sources;
  \item The majority of the recovered magnetic parameters have considerably low errors, especially in the directions, usually less than 5° (Figure~\ref{complex-synthetic-comparison}a);
  \item The magnetic moments obtained from well-individualized sources tend to not deviate much from the real values (Figure~\ref{complex-synthetic-comparison}b) when $R^2$ and SNR scores are considered high ($\geq 0.85$ and $\geq 5$, respectively) (Figure~\ref{complex-synthetic-comparison}c-d);
  \item Shallow particles grouped in clusters are usually well individualized during window selection; as well as
  \item Some isolated particles that produce a weak magnetic signal.
\end{enumerate}

It is clear from the error bars in Figure~\ref{complex-synthetic-comparison} that deep-seated sources and/or particles with small dipole moments generate worse results, essentially because they will produce weaker anomalous fields in the magnetic maps.
Note nonetheless, that even sources with small dipole moments when close to the surface are adequately modeled by our method, because of the trade-off between signal and noise for grains near the sensor. So we can point out the major limitations observed were: 
% (i) the blob detection fails when there are sources too close, grouping them into the same window, thus causing an erroneous result both for Euler deconvolution and for the magnetic parameters.
% (ii) The very same occurs when there is a source under another, in this case, the magnetic signal is the sum of both.
% (iii) In clusters of larger and/or deeper particles, although the method individualizes them well, the magnetic signal of the neighboring particles can considerably influence the result of the inversion, especially the estimated dipole moment (cluster in the Figure~\ref{complex-synthetic-comparison}b with the highest misfit values).
% As expected, there is a direct relationship between the dipole intensity and depth with the observed errors.
